Pilot Analysis (music perception study)

### 2021-01-21 analysis/analysis.Rmd
update pilot analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Individual data
```{r summary, echo = FALSE}
# remove irrelevant strings
data$midFile <- gsub("./practice/", "", data$midFile)
data$midFile <- gsub("./mid/", "", data$midFile)
data$midFile <- gsub(".mid", "", data$midFile)

# name conditions
data$condition <- "NA"
data$technique <- "NA"
data[grepl("_t_", midFile)]$condition <- "teaching"
data[grepl("_p_", midFile)]$condition <- "performing"
data[grepl("a_", midFile)]$technique <- "articulation"
data[grepl("d_", midFile)]$technique <- "dynamics"
# check correct or incorrect
data$correct <- 0
data[condition == "teaching" & rating == "Yes"]$correct <- 1
data[condition == "performing" & rating == "No"]$correct <- 1

@@

## Accuracy
### All
```{r acc, echo = FALSE}
# individual
ind_data <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data <- ind_data[order(subjectNumber)]

# all
subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
subset
```
### articulation
```{r acc-a, echo = FALSE}
# individual
ind_data_a <- data[expMode == "experiment" & technique == "articulation" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data_a <- ind_data_a[order(subjectNumber)]

# all
subset_a <- ind_data_a[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100)]
subset_a
```

### dynamics
```{r acc-d, echo = FALSE}
# individual
ind_data_d <- data[expMode == "experiment" & technique == "dynamics" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data_d <- ind_data_d[order(subjectNumber)]

# all
subset_d <- ind_data_d[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/48)*100, SD_Percent = (sd(Sum)/48)*100)]
subset_d
```

@@

## 3. teaching (each item)
```{r item1, echo = FALSE}
# individual
ind_data3 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "teaching", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, midFile)]
ind_data3 <- ind_data3[order(subjectNumber, condition, technique, midFile)]

# all
subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, midFile)]
subset3[order(-Mean_Percent)]

bar <- ggplot(subset3, aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar
```

@@

bar_a <- ggplot(subset3[technique == "articulation"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar_a
```

### dynamics
```{r item1-d, echo = FALSE}
subset3_b <- subset3[order(-Mean_Percent) & technique == "dynamics"]
subset3_b[order(-Mean_Percent)]

bar_d <- ggplot(subset3[technique == "dynamics"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar_d
```

## 3. performing (each item)
```{r item2, echo = FALSE}
# individual
ind_data4 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "performing", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, midFile)]
ind_data4 <- ind_data4[order(subjectNumber, condition, technique, midFile)]

# all
subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, midFile)]
subset4[order(-Mean_Percent)]

bar2 <- ggplot(subset4, aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar2
```

@@

bar2_a <- ggplot(subset4[technique == "articulation"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar2_a
```

@@

bar2_d <- ggplot(subset4[technique == "dynamics"], aes(x = reorder(midFile, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity")
bar2_d
```

>>>>

# Accuracy
## Individual data
```{r summary, echo = FALSE}
# remove irrelevant strings
data$midFile <- gsub("./practice/", "", data$midFile)
data$midFile <- gsub("./mid/", "", data$midFile)
data$midFile <- gsub(".mid", "", data$midFile)

# name conditions
data$condition <- "NA"
data$technique <- "NA"
data[grepl("_t_", midFile)]$condition <- "teaching"
data[grepl("_p_", midFile)]$condition <- "performing"
data[grepl("a_", midFile)]$technique <- "articulation"
data[grepl("d_", midFile)]$technique <- "dynamics"
data$item <- gsub("a_t_", "", data$midFile)
data$item <- gsub("d_t_", "", data$item)
data$item <- gsub("a_p_", "", data$item)
data$item <- gsub("d_p_", "", data$item)

# check correct or incorrect
data$correct <- 0
data[condition == "teaching" & rating == "Yes"]$correct <- 1
data[condition == "performing" & rating == "No"]$correct <- 1

@@

## Summary
### all
```{r acc, echo = FALSE}
# individual
ind_data <- data[expMode == "experiment" & subjectNumber != 9, .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber)]
ind_data <- ind_data[order(subjectNumber)]

# all
subset <- ind_data[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum)/96)*100, SD_Percent = (sd(Sum)/96)*100)]
subset
```
### articulation vs. dynamics

@@

## 3. teaching (each item)
```{r item1, echo = FALSE}
# individual
ind_data3 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "teaching", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, item)]
ind_data3 <- ind_data3[order(subjectNumber, condition, technique, item)]

# all
subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, item)]
subset3[order(-Mean_Percent)]
```

@@

bar_a <- ggplot(subset3[technique == "articulation"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
bar_a
```

### dynamics
```{r item1-d, echo = FALSE}
subset3_d <- subset3[order(-Mean_Percent) & technique == "dynamics"]
subset3_d[order(-Mean_Percent)]

bar_d <- ggplot(subset3[technique == "dynamics"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
bar_d
```

## 3. performing (each item)
```{r item2, echo = FALSE}
# individual
ind_data4 <- data[expMode == "experiment" & subjectNumber != 9 & condition == "performing", .(N = .N, Sum = sum(correct), Percent = (sum(correct)/.N)*100), by = .(subjectNumber, condition, technique, item)]
ind_data4 <- ind_data4[order(subjectNumber, condition, technique, item)]

# all
subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(condition, technique, item)]
subset4[order(-Mean_Percent)]
```

@@

bar2_a <- ggplot(subset4[technique == "articulation"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
bar2_a
```

@@

bar2_d <- ggplot(subset4[technique == "dynamics"], aes(x = reorder(item, Mean_Percent), y = Mean_Percent)) + geom_bar(stat = "identity") + labs(x = "Stimuli", y = "Correct %")
bar2_d
```

```{r export, include = FALSE}
order_data <- rbind(
  data.table(subset3_a$condition, subset3_a$technique, subset3_a$item, subset3_a$Mean_Percent),
  data.table(subset3_d$condition, subset3_d$technique, subset3_d$item, subset3_d$Mean_Percent),
  data.table(subset4_a$condition, subset4_a$technique, subset4_a$item, subset4_a$Mean_Percent),
  data.table(subset4_d$condition, subset4_d$technique, subset4_d$item, subset4_d$Mean_Percent))

colnames(order_data) <- c("condition", "technique", "item", "mean_percent")

# export
fwrite(order_data, file = "order_data.txt")
```
